---
title: "DataProductsWeek2"
author: "rmydeen"
date: "5/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions
Create a web page using R Markdown that features a map created with Leaflet for Week 2 assignment for Data Products module.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

## Review criteria
The rubric contains the following two questions:

Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
Does the web page feature an interactive map that appears to have been created with Leaflet?

## Summary

This assignment creates landmark in India for tourist attractions near Bengaluru called silicon valley of India.

First plot creates landmark around Bengaluru and second one creates cluster of attractions in Karnataka State in India where Bengaluru City located.

```{r echo=FALSE}
library(leaflet)
library(knitr)
library(dplyr)
```

This map shows tourist attractions in Bengaluru City,Karnataka State in India.

### Bangalore Attractions
- Lalbagh Garden
- Fort
- Palace
- Planetarium
- Cubbon Park
- Vidhana Soudha

Popup links will point to wiki pages to provide details

```{r echo=FALSE}
blr_attractions <- leaflet() %>% 
  addTiles() %>%  # Default OpenStreetMap map tiles
  addMarkers(lat=12.9507484, lng=77.5825886, popup='<a href="https://en.wikipedia.org/wiki/Lal_Bagh">Lalbagh Botanical Garden, Bengaluru</a>') %>%
  addMarkers(lat=12.9629061,lng=77.5738578, popup='<a href="https://en.wikipedia.org/wiki/Bangalore_Fort">Bangalore Fort, Bengaluru') %>%
  addMarkers(lat=12.9987182,lng=77.5899305, popup='<a href="https://en.wikipedia.org/wiki/Bangalore_Palace">Bangalore Palace, Bengaluru') %>%
  addMarkers(lat=12.9848717,lng=77.5874454, popup='<a href="https://en.wikipedia.org/wiki/Nehru_Planetarium">Jawaharlal Nehru Planetarium,Bengaluru') %>%
  addMarkers(lat=12.9763654,lng=77.5907208, popup='<a href="https://en.wikipedia.org/wiki/Cubbon_Park">Cubbon Park, Bengaluru') %>%
  addMarkers(lat=12.9796786,lng=77.5890556, popup='<a href="https://en.wikipedia.org/wiki/Vidhana_Soudha">Suvarna Vidhana Soudha, Bengaluru')

  
blr_attractions  # Print the map for Bengaluru attractions
```

## Cluster of Location in and around Karnataka - 100
Samples from below co-ordinates picked
12.3028262,76.6525193 - Mysuru Palace
12.9763654,77.5907208 - Cubbon Park
15.3332002,76.4589573 - Humpi
```{r echo=TRUE}
#12.3028262,76.6525193 - Mysuru Palace
# 12.9763654,77.5907208 - Cubbon Park
#15.3332002,76.4589573 - Humpi
karnataka_cluster <- data.frame(lat=runif(100, min=12.30, max =15.35 ),
                 lng=runif(100, min=76.42, max = 77.60 ))  

```
```{r echo=TRUE}
karnataka_cluster %>%
leaflet() %>%
addTiles() %>%  
addMarkers(clusterOptions = markerClusterOptions()) 
```

## Summary
Above plot depicts Bengaluru tourist attractions and random locations in karnataka for assignment.